A Bayesian approach to  uncertainty in word embedding bias estimation

### 2023-10-20 paper/earlyDraft/paperDraft.Rmd
cleaning repo

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')
library("viridis") 
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(dplyr)
library(dagitty)
library(tidyverse)
library(magrittr)
library(kableExtra)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(rethinking)
library(latex2exp)
library(Hmisc)
library(grid)

>>>>

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../../')
library("viridis") 
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(dplyr)
library(dagitty)
library(tidyverse)
library(magrittr)
library(kableExtra)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(rethinking)
library(latex2exp)
library(Hmisc)
library(grid)
